---
title: "Web Scraping Using R Programming"
output: html_notebook
---
This is a IMDB Web Scraping Project in which we take data from the IMDB website on top 100 Action IMDB rated movies.

(https://www.imdb.com/search/title/?title_type=feature&num_votes=25000,&genres=action&sort=user_rating,desc&start=01&ref_=adv_nxt)

The following packages are required in order to extract data from the website.

```{r}
install.packages("rvest")
install.packages("tidyverse")
install.packages("openxlsx")
install.packages("rio")
install_formats()
```

Then we have call these packages through library function.

```{r}
library(rvest)
library(tidyverse)
library(openxlsx)
library(rio)
```

Since we need only first 100 movies, and the website contains only 50 movies per page. I used for loop to get data from 2 pages.

```{r}

imdb_table=data.frame()

for(page in seq(from = 1, to = 51, by= 50))
  {
  imdb_link=paste0("https://www.imdb.com/search/title/?title_type=feature&num_votes=25000,&genres=action&sort=user_rating,desc&start=",page,"&ref_=adv_nxt")
  imdb_page=read_html(imdb_link)
  
  Name=imdb_page %>% html_nodes(".lister-item-header a") %>% html_text()
  Year=imdb_page %>% html_nodes(".text-muted.unbold") %>% html_text()
  Genre=imdb_page %>% html_nodes(".genre") %>% html_text()
  Rating=imdb_page %>% html_nodes(".ratings-imdb-rating strong") %>% html_text()
  Runtime=imdb_page %>% html_nodes(".runtime") %>% html_text()
  Synopsis=imdb_page %>% html_nodes(".ratings-bar+ .text-muted") %>% html_text()
  Director=imdb_page %>% html_nodes(".text-muted+ p a:nth-child(1)") %>% html_text()
  imdb_table= rbind(imdb_table,data.frame(Name,Year,Genre,Rating,Runtime,Synopsis,Director)) 
}
```

Lets view the table

```{r}
view(imdb_table)
```

To export the table into a .xlsx file 

```{r}
export(imdb_table, "IMDB_Movies.xlsx")
```

The resulting .xlsx file is also available in the folder.